\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-08-31 manuscript.Rmd

BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
totR = length(LB)*(length(LB)-1)/2
A <- print (BigR/totR)*100

@@

Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items. some of the items were skewed with high Kurtosis values. The Shapiro-Wilk test of normality [@shapiroAnalysisVarianceTest1965] indicated all the items violated normality assumptions. Multivariate normality assumptions were investigated by Marida's test [@mardiaMeasuresMultivariateSkewness1970]. Multivariate skew = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis = `r printnum(mardia$b2p)` (p <0.001) indicated  multivariate normality assumptions violation. Due to these violations and ordinal nature of the response data  polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018]. Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA. However only `r apa(((BigR/totR)*100), 2,T)`% of the inter-item correlation coefficients were greater than .30 in the obtained matrix. The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`. The corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.

@@

Scree plot ( Fig\@ref(fig:fac.id)) suggested a six-factor solution.Horn's parallel analysis [@hornRationaleTestNumber1965], like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model. In our data set parallel analysis with 500 iterations indicated six-factor solution. However, In MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution.

@@

>>>>

BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
totR = length(LB)*(length(LB)-1)/2
cor.per <- print (BigR/totR)*100

@@

Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items. some of the items were skewed with high Kurtosis values. The Shapiro-Wilk test of normality [@shapiroAnalysisVarianceTest1965] indicated all the items violated normality assumptions. Multivariate normality assumptions were investigated by Marida's test [@mardiaMeasuresMultivariateSkewness1970]. Multivariate skew = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis = `r printnum(mardia$b2p)` (p <0.001) indicated  multivariate normality assumptions violation. Due to these violations and ordinal nature of the response data  polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018]. Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA. However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30 in the obtained matrix. The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`. The corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.

@@

Scree plot ( Fig\@ref(fig:fac.id)) suggested a six-factor solution.Horn's parallel analysis [@hornRationaleTestNumber1965], like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model. In our data set parallel analysis with 500 iterations indicated six-factor solution. However, In MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution. As a result, we tested both five factor and six factor solutions.

@@

```{r EFA, include=FALSE}
fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
A <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.1 <- dplyr::select(LB ,
                                    - c(item20,item17,item3, item15,item40, item4,item11, item39,
                                        item18, item45, item29, item25, item8, item46 ))

correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct = 0)

fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
B <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.2 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
                                           item18, item45, item29, item25, item8, item46,
                                           item33, item12,item31, item37,
                                           item22, item38, item6, item48))
correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)

fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

C <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.3 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
                                           item18, item45, item29, item25, item8, item46,
                                           item33, item12,item31, item37,
                                           item22, item38, item6, item48, item9, item42,
                                           item23))
correlations.red.5F.3 <- polychoric(reduced.model.5F.3,correct = 0)

fa.5F.4 <- fa(r=correlations.red.5F.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

D <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)

```{r TabEFA5, results='asis'}
Fac.5 <- fa.5F.4 
Factorloading <- cbind(Fac.5$loadings, Fac.5$communality)
colnames(Factorloading)= c("F1", "F2","F3", "F4", "F5", "Communalities")
apa_table(unclass(Factorloading))
```

```{r communalities, include=FALSE}
min.com <- min(Fac.5$communality)
max.com <- max(Fac.5$communality)
```

The initial five-factor solution with all 48 items showed the presence of cross-loading items (item 42, 16, & 1) and poor factor loading (<.30) items (item 20,3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , & 46). At first we discard the items with poor  factor loading and ran another EFA on the remaining 34 items. This iteration of EFA also appeared as a misfit in terms of poor factor loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) . Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model. Finally, a five-factor EFA solution with 23 items was accepted with RMSR = 0.04, no loading smaller than .30 and no cross-loading greater than .30. The communalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. The histogram of the absolute values of non-redundant residual-correlations showed  correlations greater than the absolute value of .05 is ------[@desjardinsHandbookEducationalMeasurement2018a].
```{r FivRes, out.height= "50%",  fig.align='center', fig.cap=' Residulas of five-dactor solution'}
residual.5F =residuals(fa.5F.4, diag = FALSE, na.rm =T)
hist(residual.5F, col ="red", main = NULL, xlab = "Five factor oblique rotation: Residuals",ylim=c(0, 300))
abline(h =48, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)
```

### 2021-08-31 manuscript.tex

Scree plot ( Fig@ref(fig:fac.id)) suggested a six-factor solution.Horn's parallel analysis (Horn, 1965), like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model. In our data set parallel analysis with 500 iterations indicated six-factor solution. However, In MAP method (Velicer, 1976) and Hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) suggested a five-factor solution Parallel analysis is also more immune to the normality assumptions violation(\textbf{RN1263?}).

@@

@@

>>>>

Scree plot ( Fig@ref(fig:fac.id)) suggested a six-factor solution.Horn's parallel analysis (Horn, 1965), like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model. In our data set parallel analysis with 500 iterations indicated six-factor solution. However, In MAP method (Velicer, 1976) and Hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) suggested a five-factor solution. As a result, we tested both five factor and six factor solutions. The histogram of the absolute values of non-redundant residual-correlations the proportion of non-redundant residual correlations greater than the absolute value of .05 should be small

@@

\caption{\label{tab:TabEFA5}}

\begin{tabular}{lllllll}
\toprule
 & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{F2} & \multicolumn{1}{c}{F3} & \multicolumn{1}{c}{F4} & \multicolumn{1}{c}{F5} & \multicolumn{1}{c}{Communalities}\\
\midrule
item1 & 0.06 & -0.03 & 0.01 & 0.03 & 0.35 & 0.13\\
item2 & 0.12 & -0.10 & -0.11 & 0.69 & -0.03 & 0.51\\
item5 & 0.01 & 0.16 & 0.09 & 0.01 & 0.69 & 0.52\\
item7 & 0.06 & -0.09 & 0.66 & -0.01 & -0.03 & 0.45\\
item10 & -0.01 & 0.82 & 0.07 & 0.02 & 0.02 & 0.68\\
item13 & -0.06 & 0.34 & -0.03 & 0.10 & 0.00 & 0.13\\
item14 & 0.00 & 0.05 & 0.89 & -0.08 & -0.08 & 0.81\\
item16 & 0.10 & 0.05 & 0.29 & -0.11 & 0.31 & 0.21\\
item19 & 0.02 & -0.06 & 0.00 & 0.80 & 0.03 & 0.64\\
item21 & -0.05 & -0.02 & -0.34 & 0.03 & -0.06 & 0.12\\
item24 & -0.03 & 0.10 & 0.10 & 0.11 & 0.54 & 0.33\\
item26 & 0.93 & 0.00 & 0.13 & -0.01 & 0.13 & 0.90\\
item27 & -0.01 & 0.07 & 0.38 & -0.12 & 0.21 & 0.21\\
item28 & 0.02 & 0.00 & -0.05 & 0.01 & 0.31 & 0.10\\
item30 & 0.06 & 0.01 & 0.11 & -0.04 & 0.52 & 0.29\\
item32 & 0.80 & 0.00 & 0.05 & 0.13 & 0.10 & 0.67\\
item34 & -0.01 & -0.14 & 0.02 & 0.84 & 0.12 & 0.74\\
item35 & -0.04 & 0.46 & 0.04 & -0.17 & 0.04 & 0.25\\
item36 & 0.09 & 0.63 & 0.10 & -0.15 & 0.11 & 0.45\\
item41 & 0.05 & 0.07 & 0.70 & 0.30 & 0.14 & 0.60\\
item43 & 0.99 & 0.00 & 0.06 & 0.01 & 0.03 & 0.99\\
item44 & -0.03 & -0.47 & -0.01 & 0.10 & 0.01 & 0.24\\
item47 & 0.02 & 0.82 & -0.05 & -0.06 & 0.16 & 0.70\\
\bottomrule
\end{tabular}

The initial five-factor solution with all 48 items showed the presence of cross-loading items (item 42, 16, \& 1) and poor factor loading (\textless.30) items (item 20,3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , \& 46). At first we discard the items with poor factor loading and ran another EFA on the remaining 34 items. This iteration of EFA also appeared as a misfit in terms of poor factor loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) . Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model. Finally, a five-factor EFA solution with 23 items was accepted with RMSR = 0.04, no loading smaller than .30 and no cross-loading greater than .30.

{\centering \includegraphics[height=0.5\textheight]{manuscript_files/figure-latex/FivRes-1}

\caption{ Residulas of five-dactor solution}\label{fig:FivRes}
\end{figure}

@@

\leavevmode\hypertarget{ref-R-shiny}{}%
Chang, W., Cheng, J., Allaire, J., Sievert, C., Schloerke, B., Xie, Y., \ldots{} Borges, B. (2021). \emph{Shiny: Web application framework for r}. Retrieved from \url{https://CRAN.R-project.org/package=shiny}
